\huge A Usability Evaluation of Tor Launcher

### 2017-03-14 pets2017-paper/pets2017-paper.tex
Add link for VLC.

\subsection{Procedure} 
We ran the experiment in a meeting room at UC Berkeley. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment. Prior to each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

@@

\subsection{Procedure}
We ran our experiment at the Xlab~\cite{xlab}, an experimental social science laboratory. The room had 36 workstations with identical Windows~7 laptops. Workstation partitions discouraged participants from looking at other screens. We automatically reverted the computers to the same image at the beginning of each session. Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording. We instrumented Tor Browser to log user interactions. We manually assigned each computer to one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.

>>>>

\subsection{Procedure} 
We ran the experiment in a meeting room at UC Berkeley. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC media player~\cite{vlc} to record the screen during the experiment. Prior to each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

@@

\subsection{Procedure}
We ran our experiment at the Xlab~\cite{xlab}, an experimental social science laboratory. The room had 36 workstations with identical Windows~7 laptops. Workstation partitions discouraged participants from looking at other screens. We automatically reverted the computers to the same image at the beginning of each session. Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording. We instrumented Tor Browser to log user interactions. We manually assigned each computer to one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.
